### 2018-08-10 CS761-RandomizedAlgorithms/assignments/final.tex
problem 7

%Problem 8
\newpage
\section{}

>>>>

Choose $c = 1$. Let $U = \{u_1,\dots, u_n\}$ be a set of ground elements, and let $S_1, \dots, S_m \subseteq U$ be a set of subsets of $U$ such that $|S_i| = \frac{n}{2}$ for all $i\in [m]$. Consider a uniform random coloring of the elements of $U$ either red or blue. For each $i \in [n]$ let $R_i$ be an indicator random variable for the event that $u_i$ is colored red, and similarly let $B_i$ be an indicator random variable for the event that $u_i$ is colored blue. For each $j \in [m]$ let $$X^j := \sum_{u_i \in S_j} R_i - \sum_{u_i \in S_j} B_i.$$
Then showing $S_j$ has between $\frac{n}{4} - c\sqrt{n\log m}$ and $\frac{n}{4} +c\sqrt{n\log m}$ red elements is equivalent to showing $$|X^j| \leq 2c\sqrt{n\log m}.$$
For each $i \in [n]$ let $X_i$ be a random variable such that $X_i = 1$ if $u_i$ is red and $X_i = -1$ if $u_i$ is  blue. Since each $S_j$ has $\frac{n}{2}$ elements, each $X^j$ is the sum of exactly $\frac{n}{2}$ such $X_i$. Using Corollary $4.8$ in Probability and Computing by Mitzenmacher and Upfal we have
\begin{align*}
Pr(|X^j| \geq 2c\sqrt{n\log m}) &\leq 2e^\frac{-(2c\sqrt{n\log m})^2}{2\frac{n}{2}} \\
&= 2e^{-4c^2\log m}\\
&=\frac{2}{m^4}\\
&< \frac{1}{m} &\text{ (since $m \geq 2$, otherwise the problem is trivial)}.
\end{align*}
Then, applying a union bound,  the probability that there exists $j\in[m]$ such that $|X^j| \geq 2c\sqrt{n\log m}$ is strictly less than $1$. Thus with positive probability, for all $j\in [m]$ $$|X^j| \leq 2c\sqrt{n\log m}$$
as desired.$\blacksquare$
%Problem 8
